### 2024-07-10 cognitive-bias.qmd
20240710 - confirmation bias

>>>>

*Confirmation bias* is the tendency for people to search for, interpret, and remember information that confirms one's beliefs, as opposed to information that might disconfirm one's beliefs.
The result of confirmation bias is that people are unlikely to change their minds about something that they have a pre-existing belief about, because they tend to look only for information that supports their pre-existing beliefs.
For instance, if you believe that a particular player is a strong breakout candidate to be a sleeper, you may be more likely to pay attention to evidence that supports that the player will breakout and may be less likely to pay attention to evidence that indicates the player may struggle.
